---
title: "Case Study Group 07"
author: "Domenica Ginnette Ruales Cevallos, Rhesa Edrick Tendean, Oleksandr Soboliev, Ines Kueta Notsa"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of Study Case

A large car dealership is about to open a new branch in Dortmund. We are tasked to select the choice of cars between OEM1 and OEM2. The goal of this new car dealership selection is to increase the sales figure after a long period of low sales. For this, our team must analyze the registrations of the last three years from 2014 until 2016. In this selection, neighboring towns of Bochum Gelsenkirchen, Hilden and Nordkirchen should be considered. Important criterias for this selection are sales figures and susceptibility to errors.

## Libraries

At first, we need to install and load the package `install.load` to ease the loading process of relevant packages, that are used in this study case.

```{r message = FALSE, warning = FALSE}
if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}


install_load("tidyverse", "lubridate", "plotly", "shiny", "leaflet", "data.table")

if ("fitdistrplus" %in% (.packages())){
detach(package: fitdistrplus, unload = TRUE)
}

if ("fitdistrplus" %in% (.packages())){
detach(package: MASS, unload = TRUE)
}

if ("fitdistrplus" %in% (.packages())){
detach(package: stats, unload = TRUE)
}

```

## 0. Functions
Merge .x and .y columns of a component dataset
```{r message = FALSE, warning = FALSE}
merge_xy <- function(data) {
  data_x <- data[,1:2] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_y <- data[,3:4] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  
  data <- bind_rows(data_x, data_y)
}
```

Merge 3 columns of a component dataset
```{r message = FALSE, warning = FALSE}
merge_xyz <- function(data) {
  data_x <- data[,1:2] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_y <- data[,3:4] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_z <- data[,5:6] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  
  data <- bind_rows(data_x, data_y, data_z)
}
```

Reformat component list with 5 variables into 6 variables
```{r message = FALSE, warning = FALSE}
reformat_5 <- function(data) {
  data <- data %>% 
    mutate(ID_T_5 = NA) %>% 
    select(5, 1:4, 6) %>% 
    rename(ID_K = 1, ID_T_1 = 2, ID_T_2 = 3, ID_T_3 = 4, ID_T_4 = 5, ID_T_5 = 6)
}
```

Reformat component list with 4 variables into 6 variables
```{r message = FALSE, warning = FALSE}
reformat_4 <- function(data) {
  data <- data %>% 
    mutate(ID_T_4 = NA, ID_T_5 = NA) %>% 
    select(4, 1:3, 5:6) %>% 
    rename(ID_K = 1, ID_T_1 = 2, ID_T_2 = 3, ID_T_3 = 4, ID_T_4 = 5, ID_T_5 = 6)
}
```

## 1. Import all relevant datasets

Importing of all vehicles from OEM1 and 2. Relevant columns: ID_Fahrzeug, Herstellernummer, Fehlerhaft

```{r message = FALSE, warning = FALSE}
fahrzeuge_oem1_typ11 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ11.csv") %>% select(3, 5, 7)
fahrzeuge_oem1_typ12 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ12.csv") %>% select(3, 5, 7)
fahrzeuge_oem2_typ21 <- fread("Data/Fahrzeug/Fahrzeuge_OEM2_Typ21.csv") %>% select(3, 4, 6)
fahrzeuge_oem2_typ22 <- fread("Data/Fahrzeug/Fahrzeuge_OEM2_Typ22.csv") %>% select(3, 4, 6)

```

Importing of registered vehicles (Zulassungen_alle_Fahrzeuge.csv): ID_Nummer, Gemeinden, Zulassung
```{r message = FALSE, warning = FALSE}
zulassungen <- fread("Data/Zulassungen/Zulassungen_alle_Fahrzeuge.csv") %>% select(-1)

```

Importing component list of all vehicles (Bestandteile Fahrzeuge *): ID_Fahrzeug, ID_Karosserie, ID_Schaltung, ID_Sitze, ID_Motor

```{r message = FALSE, warning = FALSE}
bestandteile_fahrzeuge_oem1_typ11 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ11.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem1_typ12 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ12.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem2_typ21 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM2_Typ21.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem2_typ22 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM2_Typ22.csv", header = TRUE) %>% 
  select(6, 2:5)
```

Importing component K1* (Motor): ID_Motor, Fehlerhaft

```{r message = FALSE, warning = FALSE}
# Motor Dataset
komponente_k1be1 <- fread("Data/Komponente/Komponente_K1BE1.csv") %>% select(3,6)

komponente_k1be2 <- fread("Data/Komponente/Komponente_K1BE2.csv") %>% select(3,6)

komponente_k1di1 <- fread("Data/Komponente/Komponente_K1DI1.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_Motor = V1, Fehlerhaft = V2)

komponente_k1di2 <- read_file("Data/Komponente/Komponente_K1DI2.txt") %>% 
  str_replace_all("\t", "\n") %>% 
  fread(sep = "\\") %>% 
  select(3,6)
```

Importing component K2* (Sitze): ID_Sitze, Fehlerhaft

```{r message = FALSE, warning = FALSE}
# Sitze Dataset
komponente_k2le1 <- read_file("Data/Komponente/Komponente_K2LE1.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>% 
  str_replace_all("II", ";") %>% 
  fread() %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Sitze = V1, Fehlerhaft = V2)

komponente_k2le2 <- fread("Data/Komponente/Komponente_K2LE2.txt", sep = "\\") %>% select(3,6)

komponente_k2st1 <- fread("Data/Komponente/Komponente_K2ST1.txt") %>% select(3,7)

komponente_k2st2 <- fread("Data/Komponente/Komponente_K2ST2.csv") %>% select(3,6)
```

Importing component K3* (Schaltung): ID_Schaltung, Fehlerhaft
```{r message = FALSE, warning = FALSE}
# Schaltung Dataset
komponente_k3ag1 <- fread("Data/Komponente/Komponente_K3AG1.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_Schaltung = V1, Fehlerhaft = V2)

komponente_k3ag2 <- fread("Data/Komponente/Komponente_K3AG2.txt", sep = "\\") %>% select(3,6)

komponente_k3sg1 <- fread("Data/Komponente/Komponente_K3SG1.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Schaltung = V1, Fehlerhaft = V2)

komponente_k3sg2 <- fread("Data/Komponente/Komponente_K3SG2.csv") %>% select(3,6)
```

Importing component K4 - K7 (Karosserie): ID_Karosserie, Fehlerhaft
```{r message = FALSE, warning = FALSE}
# Karosserie Dataset
komponente_k4 <- fread("Data/Komponente/Komponente_K4.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Karosserie = V1, Fehlerhaft = V2)

komponente_k5 <- fread("Data/Komponente/Komponente_K5.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Karosserie = V1, Fehlerhaft = V2)

komponente_k6 <- fread("Data/Komponente/Komponente_K6.csv") %>% select(3,6)
komponente_k7 <- fread("Data/Komponente/Komponente_K7.txt") %>% select(3,6)
```

Importing list of single components (Bestandteile Komponente *)

```{r message = FALSE, warning = FALSE}
# Component List of each components
bestandteile_komponente_k1be1 <- fread("Data/Komponente/Bestandteile_Komponente_K1BE1.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k1be2 <- fread("Data/Komponente/Bestandteile_Komponente_K1BE2.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k1di1 <- fread("Data/Komponente/Bestandteile_Komponente_K1DI1.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k1di2 <- fread("Data/Komponente/Bestandteile_Komponente_K1DI2.csv", header = TRUE) %>% 
  select(-1)

bestandteile_komponente_k2le1 <- fread("Data/Komponente/Bestandteile_Komponente_K2LE1.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k2le2 <- fread("Data/Komponente/Bestandteile_Komponente_K2LE2.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k2st1 <- fread("Data/Komponente/Bestandteile_Komponente_K2ST1.csv", header = TRUE) %>% 
  select(-c(1,2))
bestandteile_komponente_k2st2 <- fread("Data/Komponente/Bestandteile_Komponente_K2ST2.csv", header = TRUE) %>% 
  select(-1)

bestandteile_komponente_k3ag1 <- fread("Data/Komponente/Bestandteile_Komponente_K3AG1.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k3ag2 <- fread("Data/Komponente/Bestandteile_Komponente_K3AG2.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k3sg1 <- fread("Data/Komponente/Bestandteile_Komponente_K3SG1.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k3sg2 <- fread("Data/Komponente/Bestandteile_Komponente_K3SG2.csv", header = TRUE) %>% 
  select(-1)

bestandteile_komponente_k4 <- fread("Data/Komponente/Bestandteile_Komponente_K4.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k5 <- fread("Data/Komponente/Bestandteile_Komponente_K5.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k6 <- fread("Data/Komponente/Bestandteile_Komponente_K6.csv", header = TRUE) %>% 
  select(-1)
bestandteile_komponente_k7 <- fread("Data/Komponente/Bestandteile_Komponente_K7.csv", header = TRUE) %>% 
  select(-1)

```

Importing all single components (Einzelteil): ID_, Fehlerhaft

```{r message = FALSE, warning = FALSE}
# Single component dataset
einzelteil_t01 <- read_file("Data/Einzelteil/Einzelteil_T01.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>%
  str_replace_all(" ", "\n") %>% 
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T01 = V1, Fehlerhaft = V2)

einzelteil_t02 <- read_file("Data/Einzelteil/Einzelteil_T02.txt") %>% 
  str_replace_all("\t", "\n") %>%
  str_replace_all("  ", ";") %>% 
  fread() %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T02 = V1, Fehlerhaft = V2)

einzelteil_t03 <- read_file("Data/Einzelteil/Einzelteil_T03.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  str_replace_all("\\|", ";") %>%
  fread() %>% 
  select(3,6)

einzelteil_t04 <- fread("Data/Einzelteil/Einzelteil_T04.csv") %>% select(3,6)

einzelteil_t05 <- fread("Data/Einzelteil/Einzelteil_T05.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T05 = V1, Fehlerhaft = V2)

einzelteil_t06 <- fread("Data/Einzelteil/Einzelteil_T06.csv") %>% select(3,6)

einzelteil_t07 <- read_file("Data/Einzelteil/Einzelteil_T07.txt") %>% 
  str_replace_all("\"\"", "\"\n\"") %>% 
  fread() %>% 
  select(3,6)

einzelteil_t08 <- fread("Data/Einzelteil/Einzelteil_T08.csv") %>% select(3,6)

einzelteil_t09 <- read_file("Data/Einzelteil/Einzelteil_T09.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>% 
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T09 = V1, Fehlerhaft = V2)

einzelteil_t10 <- fread("Data/Einzelteil/Einzelteil_T10.csv") %>% select(3,6)

einzelteil_t11 <- read_file("Data/Einzelteil/Einzelteil_T11.txt") %>% 
  str_replace_all("\t", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6)

einzelteil_t12 <- fread("Data/Einzelteil/Einzelteil_T12.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T12 = V1, Fehlerhaft = V2)

einzelteil_t13 <- fread("Data/Einzelteil/Einzelteil_T13.csv", dec = ",") %>% select(3,6)

einzelteil_t14 <- fread("Data/Einzelteil/Einzelteil_T14.csv", dec = ",") %>% select(3,6)

einzelteil_t15 <- fread("Data/Einzelteil/Einzelteil_T15.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T15 = V1, Fehlerhaft = V2)

einzelteil_t16 <- read_file("Data/Einzelteil/Einzelteil_T16.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("\t", "\n") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T16 = V1, Fehlerhaft = V2)

einzelteil_t17 <- fread("Data/Einzelteil/Einzelteil_T17.csv", dec = ",") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T17 = V1, Fehlerhaft = V2)

einzelteil_t18 <- fread("Data/Einzelteil/Einzelteil_T18.csv", dec = ",") %>% select(3,6)

einzelteil_t19 <- fread("Data/Einzelteil/Einzelteil_T19.csv") %>% select(3,6)

einzelteil_t20 <- read_file("Data/Einzelteil/Einzelteil_T20.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all(" ", "\n") %>% 
  fread() %>% 
  select(3, 6)

einzelteil_t21 <- fread("Data/Einzelteil/Einzelteil_T21.csv", dec = ",") %>% select(3,6)

einzelteil_t22 <- read_file("Data/Einzelteil/Einzelteil_T22.txt") %>% 
  str_replace_all("NA\"", "\n\"") %>%
  str_replace_all("\"\"", "\"\n\"") %>%
  str_replace_all("NA\t0\"", "NA\t0\n\"") %>%
  str_replace_all("(?<=\\d)\"(?=\\d)", "\n\"") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T22 = V1, Fehlerhaft = V2)

einzelteil_t23 <- fread("Data/Einzelteil/Einzelteil_T23.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T23 = V1, Fehlerhaft = V2)

einzelteil_t24 <- read_file("Data/Einzelteil/Einzelteil_T24.txt") %>% 
  str_replace_all("   ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T24 = V1, Fehlerhaft = V2)

einzelteil_t25 <- fread("Data/Einzelteil/Einzelteil_T25.csv", dec = ",") %>% select(3,6)

einzelteil_t26 <- fread("Data/Einzelteil/Einzelteil_T26.csv", dec = ",") %>% select(3,6)

einzelteil_t27 <- read_file("Data/Einzelteil/Einzelteil_T27.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6)

einzelteil_t30 <- fread("Data/Einzelteil/Einzelteil_T30.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T30 = V1, Fehlerhaft = V2)

einzelteil_t31 <- read_file("Data/Einzelteil/Einzelteil_T31.txt") %>% 
  str_replace_all("  ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6)

einzelteil_t32 <- fread("Data/Einzelteil/Einzelteil_T32.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T32 = V1, Fehlerhaft = V2)

einzelteil_t33 <- fread("Data/Einzelteil/Einzelteil_T33.csv") %>% select(3,6)

einzelteil_t34 <- read_file("Data/Einzelteil/Einzelteil_T34.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("\"\"", "\"\n\"") %>%
  fread() %>% 
  select(3,6)

einzelteil_t35 <- read_file("Data/Einzelteil/Einzelteil_T35.txt") %>% 
  str_replace_all("\"\"", "\"\n\"") %>%
  str_replace_all("NA\"", "\n\"") %>%
  str_replace_all("(?<=\\d)\"(?=\\d)", "\n\"") %>%
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T35 = V1, Fehlerhaft = V2)

einzelteil_t36 <- read_file("Data/Einzelteil/Einzelteil_T36.txt") %>% 
  str_replace_all("  ", ";") %>% 
  str_replace_all(" ", "\n") %>%
  fread() %>% 
  select(3,6)

einzelteil_t37 <- fread("Data/Einzelteil/Einzelteil_T37.csv") %>% select(3,6)

einzelteil_t38 <- fread("Data/Einzelteil/Einzelteil_T38.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T35 = V1, Fehlerhaft = V2)

einzelteil_t39 <- read_file("Data/Einzelteil/Einzelteil_T39.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T35 = V1, Fehlerhaft = V2)

einzelteil_t40 <- fread("Data/Einzelteil/Einzelteil_T40.csv") %>% select(3,6)


```

## 2. Data preparation

### Data preparation for single component (Einzelteil)
All parts (Einzelkomponente) are joined into one single data:
```{r message = FALSE, warning = FALSE}
einzelteile_all <- rbind(einzelteil_t01,einzelteil_t02,einzelteil_t03,einzelteil_t04,einzelteil_t05,
                        einzelteil_t06,einzelteil_t07,einzelteil_t08,einzelteil_t09,einzelteil_t10,
                        einzelteil_t11,einzelteil_t12,einzelteil_t13,einzelteil_t14,einzelteil_t15,
                        einzelteil_t16,einzelteil_t17,einzelteil_t18,einzelteil_t19,einzelteil_t20,
                        einzelteil_t21,einzelteil_t22,einzelteil_t23,einzelteil_t24,einzelteil_t25,
                        einzelteil_t26,einzelteil_t27, einzelteil_t30,
                        einzelteil_t31,einzelteil_t32,einzelteil_t33,einzelteil_t34,einzelteil_t35,
                        einzelteil_t36,einzelteil_t37,einzelteil_t38,einzelteil_t39,einzelteil_t40, 
                        use.names = FALSE) %>% rename(ID_T = 1)

rm(einzelteil_t01,einzelteil_t02,einzelteil_t03,einzelteil_t04,einzelteil_t05,
   einzelteil_t06,einzelteil_t07,einzelteil_t08,einzelteil_t09,einzelteil_t10,
   einzelteil_t11,einzelteil_t12,einzelteil_t13,einzelteil_t14,einzelteil_t15,
   einzelteil_t16,einzelteil_t17,einzelteil_t18,einzelteil_t19,einzelteil_t20,
   einzelteil_t21,einzelteil_t22,einzelteil_t23,einzelteil_t24,einzelteil_t25,
   einzelteil_t26,einzelteil_t27, einzelteil_t30,
   einzelteil_t31,einzelteil_t32,einzelteil_t33,einzelteil_t34,einzelteil_t35,
   einzelteil_t36,einzelteil_t37,einzelteil_t38,einzelteil_t39,einzelteil_t40)
```

All components (Komponente) are joined into one single data:
```{r message = FALSE, warning = FALSE}
komponente_all <- rbind(komponente_k1be1, komponente_k1be2, komponente_k1di1, komponente_k1di2,
                        komponente_k2le1, komponente_k2le2, komponente_k2st1, komponente_k2st2,
                        komponente_k3ag1, komponente_k3ag2, komponente_k3sg1, komponente_k3sg2,
                        komponente_k4, komponente_k5, komponente_k6, komponente_k7,
                        use.names = FALSE) %>% rename(ID_K = 1)

rm(komponente_k1be1, komponente_k1be2, komponente_k1di1, komponente_k1di2,
   komponente_k2le1, komponente_k2le2, komponente_k2st1, komponente_k2st2,
   komponente_k3ag1, komponente_k3ag2, komponente_k3sg1, komponente_k3sg2,
   komponente_k4, komponente_k5, komponente_k6, komponente_k7)

```

All vehicle (Fahrzeuge) are joined into one single data:

```{r message = FALSE, warning = FALSE}
fahrzeuge_all <- rbind(fahrzeuge_oem1_typ11,
                       fahrzeuge_oem1_typ12,
                       fahrzeuge_oem2_typ21,
                       fahrzeuge_oem2_typ22)

rm(fahrzeuge_oem1_typ11,
   fahrzeuge_oem1_typ12,
   fahrzeuge_oem2_typ21,
   fahrzeuge_oem2_typ22)
```

All lists of component inside vehicles (Bestandteile Fahrzeuge) are joined into one single data:
```{r message = FALSE, warning = FALSE}
bestandteile_fahrzeuge_all <- rbind(bestandteile_fahrzeuge_oem1_typ11,
                                    bestandteile_fahrzeuge_oem1_typ12,
                                    bestandteile_fahrzeuge_oem2_typ21,
                                    bestandteile_fahrzeuge_oem2_typ22)

rm(bestandteile_fahrzeuge_oem1_typ11,
   bestandteile_fahrzeuge_oem1_typ12,
   bestandteile_fahrzeuge_oem2_typ21,
   bestandteile_fahrzeuge_oem2_typ22)
```

All lists of parts inside component (Bestandteile Komponente) are joined into one single data. One component has 5 single parts, the others come with either 3 or 4 single parts. To join these together into one single dataset, extra 1 or 2 columns with NA value must be added to each component list dataset.

```{r message = FALSE, warning = FALSE}

bestandteile_komponente_k1be1 <-  reformat_5(bestandteile_komponente_k1be1)
bestandteile_komponente_k1be2 <-  reformat_5(bestandteile_komponente_k1be2)
bestandteile_komponente_k1di1 <- reformat_5(bestandteile_komponente_k1di1)
bestandteile_komponente_k1di2 <- reformat_5(bestandteile_komponente_k1di2)

bestandteile_komponente_k2le1 <- reformat_4(bestandteile_komponente_k2le1)
bestandteile_komponente_k2le2 <- reformat_4(bestandteile_komponente_k2le2)
bestandteile_komponente_k2st1 <- reformat_4(bestandteile_komponente_k2st1)
bestandteile_komponente_k2st2 <- reformat_4(bestandteile_komponente_k2st2)

bestandteile_komponente_k3ag1 <- reformat_4(bestandteile_komponente_k3ag1)
bestandteile_komponente_k3ag2 <- reformat_4(bestandteile_komponente_k3ag2)
bestandteile_komponente_k3sg1 <- reformat_4(bestandteile_komponente_k3sg1)
bestandteile_komponente_k3sg2 <- reformat_4(bestandteile_komponente_k3sg2)

bestandteile_komponente_k4 <- reformat_4(bestandteile_komponente_k4)
bestandteile_komponente_k5 <- reformat_4(bestandteile_komponente_k5)
bestandteile_komponente_k6 <- reformat_5(bestandteile_komponente_k6)

bestandteile_komponente_all <- rbind(bestandteile_komponente_k1be1, bestandteile_komponente_k1be2,
                                     bestandteile_komponente_k1di1, bestandteile_komponente_k1di2,
                                     bestandteile_komponente_k2le1, bestandteile_komponente_k2le2,
                                     bestandteile_komponente_k2st1, bestandteile_komponente_k2st2,
                                     bestandteile_komponente_k3ag1, bestandteile_komponente_k3ag2,
                                     bestandteile_komponente_k3sg1, bestandteile_komponente_k3sg2,
                                     bestandteile_komponente_k4, bestandteile_komponente_k5, 
                                     bestandteile_komponente_k6, bestandteile_komponente_k7,
                                     use.names = FALSE)
rm(bestandteile_komponente_k1be1, bestandteile_komponente_k1be2,
   bestandteile_komponente_k1di1, bestandteile_komponente_k1di2,
   bestandteile_komponente_k2le1, bestandteile_komponente_k2le2,
   bestandteile_komponente_k2st1, bestandteile_komponente_k2st2,
   bestandteile_komponente_k3ag1, bestandteile_komponente_k3ag2,
   bestandteile_komponente_k3sg1, bestandteile_komponente_k3sg2,
   bestandteile_komponente_k4, bestandteile_komponente_k5, 
   bestandteile_komponente_k6, bestandteile_komponente_k7)
```


Filter vehicle registration for the year 2014 - 2016 in Dortmund, Bochum, Gelsenkirchen, Hilden and Nordkirchen.

```{r message = FALSE, warning = FALSE}
zulassungen_filter <- zulassungen %>% 
  filter(Gemeinden %in% c("DORTMUND", "BOCHUM", "GELSENKIRCHEN", "HILDEN", "NORDKIRCHEN")) %>% 
  filter(Zulassung >= "2014-01-01" & Zulassung <= "2016-12-31") %>% 
  arrange(Zulassung, IDNummer)
```

Join filtered vehicle registration with vehicle dataset, component dataset

```{r message = FALSE, warning = FALSE}
zulassungen_component <- zulassungen_filter %>% 
  left_join(fahrzeuge_all, by = c("IDNummer" = "ID_Fahrzeug")) %>% 
  rename("Defective Vehicle" = "Fehlerhaft") %>% 
  left_join(bestandteile_fahrzeuge_all, by = c("IDNummer" = "ID_Fahrzeug")) %>% 
  left_join(komponente_all, by = c("ID_Karosserie" = "ID_K")) %>% 
  rename("Defective Karosserie" = "Fehlerhaft") %>% 
  left_join(komponente_all, by = c("ID_Schaltung" = "ID_K")) %>% 
  rename("Defective Transmission" = "Fehlerhaft") %>% 
  left_join(komponente_all, by = c("ID_Sitze" = "ID_K")) %>% 
  rename("Defective Seat" = "Fehlerhaft") %>% 
  left_join(komponente_all, by = c("ID_Motor" = "ID_K")) %>% 
  rename("Defective Motor" = "Fehlerhaft")

zulassungen_component %>% filter(is.na(`Defective Motor`))
```

