---
title: "Case Study Group 07"
author: "Domenica Ginnette Ruales Cevallos, Rhesa Edrick Tendean, Oleksandr Soboliev"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of Study Case

A large car dealership is about to open a new branch in Dortmund. We are tasked to select the choice of cars between OEM1 and OEM2. The goal of this new car dealership selection is to increase the sales figure after a long period of low sales. For this, our team needs to analyze the registrations of the last three years from 2014 until 2016. In this selection, neighboring towns of Bochum Gelsenkirchen, Hilden and Nordkirchen should be considered. Important criterias for this selection are sales figures and susceptibility to errors.

In this study case, the first task would be to analyze the temporal course of sales figures for both brands in Dortmund, Bochum, Gelsenkirchen, Hilden and Nordkirchen. Secondly, we are tasked to create a figure to visualize the relative proportion of defective registered vehicles of the respective brand. Besides that, the user should also be able to recognize the relative proportion of defective component and parts. For both tasks, filtering by location and time period of registration should be possible. Afterwards, a sales forecast is required to show the development of sales figures for both brands for the next quarter which is Q1 2017. Based on this, the team must recommend the most suitable car brand.

## Libraries

At first, we need to install and load the package `install.load` to ease the loading process of relevant packages, that are used in this study case. Relevant packages are `tidyverse`, `lubridate`, `plotly`, `shiny`, `leaflet` and `data.table`. Besides that, `fitdistrplus`, `MASS` and `stats` must be unloaded due to interference with some functions from `dplyr`.

```{r message = FALSE, warning = FALSE}
if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}


install_load("tidyverse", "data.table")
library(tidyverse)
library(data.table)

if ("fitdistrplus" %in% (.packages())){
detach(package: fitdistrplus, unload = TRUE)
}

if ("fitdistrplus" %in% (.packages())){
detach(package: MASS, unload = TRUE)
}

if ("fitdistrplus" %in% (.packages())){
detach(package: stats, unload = TRUE)
}

```

## 0. Functions
Some datasets consist columns, that are repeated twice. To ease the process of data preparation, this columns should be merged. Following function is implemented:
```{r message = FALSE, warning = FALSE}
merge_xy <- function(data) {
  data_x <- data[,1:2] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_y <- data[,3:4] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  
  data <- bind_rows(data_x, data_y)
}
```

Some datasets consist columns, that are repeated three times To ease the process of data preparation, this columns should be merged. Following function is implemented:
```{r message = FALSE, warning = FALSE}
merge_xyz <- function(data) {
  data_x <- data[,1:2] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_y <- data[,3:4] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  data_z <- data[,5:6] %>% na.omit(1) %>% rename(V1 = 1, V2 = 2)
  
  data <- bind_rows(data_x, data_y, data_z)
}
```

The part list datasets (Bestandteile Komponente) contain either 3, 4, or 5 different parts. To merge all datasets into one single dataset, the datasets with only 3 and 4 different parts need to be reformated to accomodate the number of columns inside dataset with 5 parts. These extra colums are filled with `NA`.

Following function is intended to reformat part list datasets (Bestandteile Komponente) with 4 different part to accomodate datasets with 5 parts.
```{r message = FALSE, warning = FALSE}
reformat_5 <- function(data) {
  data <- data %>% 
    mutate(ID_T_5 = NA) %>% 
    select(5, 1:4, 6) %>% 
    rename(ID_K = 1, ID_T_1 = 2, ID_T_2 = 3, ID_T_3 = 4, ID_T_4 = 5, ID_T_5 = 6)
}
```

Following function is intended to reformat part list datasets (Bestandteile Komponente) with 3 different part to accomodate datasets with 5 parts.
```{r message = FALSE, warning = FALSE}
reformat_4 <- function(data) {
  data <- data %>% 
    mutate(ID_T_4 = NA, ID_T_5 = NA) %>% 
    select(4, 1:3, 5:6) %>% 
    rename(ID_K = 1, ID_T_1 = 2, ID_T_2 = 3, ID_T_3 = 4, ID_T_4 = 5, ID_T_5 = 6)
}
```

## 1. Import all relevant datasets
### Importing vehicle dataset, component list, and registeration

As explained above, the task of this study case is to analyze the number of registered vehicles from OEM1 and OEM2 within the aforementioned time frame and location and to analyze the number of their defectives on vehicle, component and single part level. The main task for importing is to extract the car id number, registration date, location, number of defective vehicles, number of defective components and number of defective single parts from the provided data.

The first step towards this analysis is to import the list of registered vehicles from `Zulassungen_alle_Fahrzeuge.csv` dataset. First column which contains number of lines is removed to reduce the size of the data.
```{r message = FALSE, warning = FALSE}
zulassungen <- fread("Data/Zulassungen/Zulassungen_alle_Fahrzeuge.csv") %>% select(-1)

```

To determine which type of vehicle from OEM1 and 2, following code is implemented.
```{r}
unique(substr(zulassungen$IDNummer, 1,4))
```
Based on this result, we need to import vehicle Type 11 and Type 12 from OEM1 and Type 21 and Type 22 from OEM2. In this case, only relevant columns are imported, which are: `ID_Fahrzeug`, `Herstellernummer`, `Fehlerhaft`.

```{r message = FALSE, warning = FALSE}
fahrzeuge_oem1_typ11 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ11.csv") %>% select(3, 5, 7)
fahrzeuge_oem1_typ12 <- fread("Data/Fahrzeug/Fahrzeuge_OEM1_Typ12.csv") %>% select(3, 5, 7)
fahrzeuge_oem2_typ21 <- fread("Data/Fahrzeug/Fahrzeuge_OEM2_Typ21.csv") %>% select(3, 4, 6)
fahrzeuge_oem2_typ22 <- fread("Data/Fahrzeug/Fahrzeuge_OEM2_Typ22.csv") %>% select(3, 4, 6)
```

To determine which component datasets are needed, we need to import component list of vehicles (Bestandteile Fahrzeuge). Relevant columns are: `ID_Fahrzeug`, `ID_Karosserie`, `ID_Schaltung`, `ID_Sitze` and `ID_Motor`.

```{r message = FALSE, warning = FALSE}
bestandteile_fahrzeuge_oem1_typ11 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ11.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem1_typ12 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ12.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem2_typ21 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM2_Typ21.csv", header = TRUE) %>% 
  select(6, 2:5)
bestandteile_fahrzeuge_oem2_typ22 <- fread("Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM2_Typ22.csv", header = TRUE) %>% 
  select(6, 2:5)
```

### Joining vehicle and component list of vehicles datasets

Vehicle datasets (Fahrzeuge) are joined into one single dataset:

```{r message = FALSE, warning = FALSE}
fahrzeuge_all <- rbind(fahrzeuge_oem1_typ11,
                       fahrzeuge_oem1_typ12,
                       fahrzeuge_oem2_typ21,
                       fahrzeuge_oem2_typ22)

rm(fahrzeuge_oem1_typ11,
   fahrzeuge_oem1_typ12,
   fahrzeuge_oem2_typ21,
   fahrzeuge_oem2_typ22)
```

Component lists of vehicles (Bestandteile Fahrzeuge) are joined into one single data:
```{r message = FALSE, warning = FALSE}
bestandteile_fahrzeuge_all <- rbind(bestandteile_fahrzeuge_oem1_typ11,
                                    bestandteile_fahrzeuge_oem1_typ12,
                                    bestandteile_fahrzeuge_oem2_typ21,
                                    bestandteile_fahrzeuge_oem2_typ22)

rm(bestandteile_fahrzeuge_oem1_typ11,
   bestandteile_fahrzeuge_oem1_typ12,
   bestandteile_fahrzeuge_oem2_typ21,
   bestandteile_fahrzeuge_oem2_typ22)
```

### Filtering registration by date and location

Vehicle registration is filtered for the year 2014 - 2016 and following location: Dortmund, Bochum, Gelsenkirchen, Hilden and Nordkirchen.

```{r message = FALSE, warning = FALSE}
zulassungen_filter <- zulassungen %>% 
  filter(Gemeinden %in% c("DORTMUND", "BOCHUM", "GELSENKIRCHEN", "HILDEN", "NORDKIRCHEN")) %>% 
  filter(Zulassung >= "2014-01-01" & Zulassung <= "2016-12-31") %>% 
  arrange(Zulassung, IDNummer)
```


### Joining filtered registration, vehicle and component list
This filtered registration data would then be joined with the combined vehicle and component dataset with `left_join()` function with `IDNummer` and `ID_Fahrzeug` column as matching criteria.

```{r message = FALSE, warning = FALSE}
zulassungen_componentList <- zulassungen_filter %>% 
  left_join(fahrzeuge_all, by = c("IDNummer" = "ID_Fahrzeug")) %>% 
  rename("Defective Vehicle" = "Fehlerhaft") %>% 
  left_join(bestandteile_fahrzeuge_all, by = c("IDNummer" = "ID_Fahrzeug"))

rm(fahrzeuge_all, zulassungen, zulassungen_filter, bestandteile_fahrzeuge_all)
```

### Finding relevant component dataset
The following code is used to find the relevant components for this study case.
```{r message = FALSE, warning = FALSE}
unique(substr(zulassungen_componentList$ID_Karosserie, 1,2))
unique(substr(zulassungen_componentList$ID_Schaltung, 1,5))
unique(substr(zulassungen_componentList$ID_Sitze, 1,5))
unique(substr(zulassungen_componentList$ID_Motor, 1,5))
```
Based on this result, all components are required to be imported. The next step is to determine, which single part datasets are required.

### Creating a list of all relevant components
```{r message = FALSE, warning = FALSE}
karosserie <- select(zulassungen_componentList, ID_Karosserie)
schaltung <- select(zulassungen_componentList, ID_Schaltung)
sitze <- select(zulassungen_componentList, ID_Sitze)
motor <- select(zulassungen_componentList, ID_Motor)

componentList <- rbind(karosserie, schaltung, sitze, motor, use.names = FALSE) %>% rename("ID_K" = 1)
rm(karosserie, schaltung, sitze, motor)
```


### Importing single part list datasets
Function `fread()` with header-value set to `TRUE` is used for importing the all single part list datasets (Bestandteile Komponente). The first column is removed to simplify the dataset.
```{r message = FALSE, warning = FALSE}
# Component List of Motor
bestandteile_komponente_k1be1 <- fread("Data/Komponente/Bestandteile_Komponente_K1BE1.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K1BE1" = "ID_K"))

bestandteile_komponente_k1be2 <- fread("Data/Komponente/Bestandteile_Komponente_K1BE2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K1BE2" = "ID_K"))

bestandteile_komponente_k1di1 <- fread("Data/Komponente/Bestandteile_Komponente_K1DI1.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K1DI1" = "ID_K"))

bestandteile_komponente_k1di2 <- fread("Data/Komponente/Bestandteile_Komponente_K1DI2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K1DI2" = "ID_K"))

# Component List of Seat
bestandteile_komponente_k2le1 <- fread("Data/Komponente/Bestandteile_Komponente_K2LE1.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K2LE1" = "ID_K"))

bestandteile_komponente_k2le2 <- fread("Data/Komponente/Bestandteile_Komponente_K2LE2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K2LE2" = "ID_K"))

bestandteile_komponente_k2st1 <- fread("Data/Komponente/Bestandteile_Komponente_K2ST1.csv", header = TRUE) %>% 
  select(-c(1,2)) %>% 
  semi_join(componentList, by = c("ID_K2ST1" = "ID_K"))

bestandteile_komponente_k2st2 <- fread("Data/Komponente/Bestandteile_Komponente_K2ST2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K2ST2" = "ID_K"))

# Component List of Transmission
bestandteile_komponente_k3ag1 <- fread("Data/Komponente/Bestandteile_Komponente_K3AG1.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K3AG1" = "ID_K"))

bestandteile_komponente_k3ag2 <- fread("Data/Komponente/Bestandteile_Komponente_K3AG2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K3AG2" = "ID_K"))

bestandteile_komponente_k3sg1 <- fread("Data/Komponente/Bestandteile_Komponente_K3SG1.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K3SG1" = "ID_K"))

bestandteile_komponente_k3sg2 <- fread("Data/Komponente/Bestandteile_Komponente_K3SG2.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K3SG2" = "ID_K"))

# Component List of Karosserie
bestandteile_komponente_k4 <- fread("Data/Komponente/Bestandteile_Komponente_K4.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K4" = "ID_K"))

bestandteile_komponente_k5 <- fread("Data/Komponente/Bestandteile_Komponente_K5.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K5" = "ID_K"))

bestandteile_komponente_k6 <- fread("Data/Komponente/Bestandteile_Komponente_K6.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K6" = "ID_K"))

bestandteile_komponente_k7 <- fread("Data/Komponente/Bestandteile_Komponente_K7.csv", header = TRUE) %>% 
  select(-1) %>% 
  semi_join(componentList, by = c("ID_K7" = "ID_K"))

```

### Joining single part lists into a single dataset
All lists of single parts inside component (Bestandteile Komponente) are joined into one single data. One component has 5 single parts, the others come with either 3 or 4 single parts. To join these together into one single dataset, extra 1 or 2 columns with NA value must be added to each component list dataset.

```{r message = FALSE, warning = FALSE}

bestandteile_komponente_k1be1 <-  reformat_5(bestandteile_komponente_k1be1)
bestandteile_komponente_k1be2 <-  reformat_5(bestandteile_komponente_k1be2)
bestandteile_komponente_k1di1 <- reformat_5(bestandteile_komponente_k1di1)
bestandteile_komponente_k1di2 <- reformat_5(bestandteile_komponente_k1di2)

bestandteile_komponente_k2le1 <- reformat_4(bestandteile_komponente_k2le1)
bestandteile_komponente_k2le2 <- reformat_4(bestandteile_komponente_k2le2)
bestandteile_komponente_k2st1 <- reformat_4(bestandteile_komponente_k2st1)
bestandteile_komponente_k2st2 <- reformat_4(bestandteile_komponente_k2st2)

bestandteile_komponente_k3ag1 <- reformat_4(bestandteile_komponente_k3ag1)
bestandteile_komponente_k3ag2 <- reformat_4(bestandteile_komponente_k3ag2)
bestandteile_komponente_k3sg1 <- reformat_4(bestandteile_komponente_k3sg1)
bestandteile_komponente_k3sg2 <- reformat_4(bestandteile_komponente_k3sg2)

bestandteile_komponente_k4 <- reformat_4(bestandteile_komponente_k4)
bestandteile_komponente_k5 <- reformat_4(bestandteile_komponente_k5)
bestandteile_komponente_k6 <- reformat_5(bestandteile_komponente_k6)
bestandteile_komponente_k7 <- bestandteile_komponente_k7 %>% select(6, 1:5)

bestandteile_komponente_all <- rbind(bestandteile_komponente_k1be1, bestandteile_komponente_k1be2,
                                     bestandteile_komponente_k1di1, bestandteile_komponente_k1di2,
                                     bestandteile_komponente_k2le1, bestandteile_komponente_k2le2,
                                     bestandteile_komponente_k2st1, bestandteile_komponente_k2st2,
                                     bestandteile_komponente_k3ag1, bestandteile_komponente_k3ag2,
                                     bestandteile_komponente_k3sg1, bestandteile_komponente_k3sg2,
                                     bestandteile_komponente_k4, bestandteile_komponente_k5, 
                                     bestandteile_komponente_k6, bestandteile_komponente_k7,
                                     use.names = FALSE)
rm(bestandteile_komponente_k1be1, bestandteile_komponente_k1be2,
   bestandteile_komponente_k1di1, bestandteile_komponente_k1di2,
   bestandteile_komponente_k2le1, bestandteile_komponente_k2le2,
   bestandteile_komponente_k2st1, bestandteile_komponente_k2st2,
   bestandteile_komponente_k3ag1, bestandteile_komponente_k3ag2,
   bestandteile_komponente_k3sg1, bestandteile_komponente_k3sg2,
   bestandteile_komponente_k4, bestandteile_komponente_k5, 
   bestandteile_komponente_k6, bestandteile_komponente_k7 
   )
```

### Joining filtered registration with whole single part list dataset
This filtered registration data would then be joined with the combined single part list dataset with `left_join()` function with `ID_K` paired with `ID_Karosserie`, `ID_Schaltung`, `ID_Sitze` and `ID_Motor` column as matching criteria. Each part id column is then renamed accordingly.The column `ID_Schaltung_T_4`, `ID_Schaltung_T_5`, `ID_Sitze_T_4` and `ID_Sitze_T_5` are removed since all transmission and seats have only 3 components. The column`ID_Motor_T_5` is removed since all motor have only 4 components.

```{r message = FALSE, warning = FALSE}
zulassungen_partList <- zulassungen_componentList %>% 
  left_join(bestandteile_komponente_all, by = c("ID_Karosserie" = "ID_K")) %>% 
  rename("ID_Karosserie_T_1" = "ID_T_1", "ID_Karosserie_T_2" = "ID_T_2", "ID_Karosserie_T_3" = "ID_T_3",
         "ID_Karosserie_T_4" = "ID_T_4", "ID_Karosserie_T_5" = "ID_T_5") %>% 
  left_join(bestandteile_komponente_all, by = c("ID_Schaltung" = "ID_K")) %>% 
  rename("ID_Schaltung_T_1" = "ID_T_1", "ID_Schaltung_T_2" = "ID_T_2", "ID_Schaltung_T_3" = "ID_T_3",
         "ID_Schaltung_T_4" = "ID_T_4", "ID_Schaltung_T_5" = "ID_T_5") %>% 
  select(-c("ID_Schaltung_T_4", "ID_Schaltung_T_5")) %>% 
  left_join(bestandteile_komponente_all, by = c("ID_Sitze" = "ID_K")) %>% 
  rename("ID_Sitze_T_1" = "ID_T_1", "ID_Sitze_T_2" = "ID_T_2", "ID_Sitze_T_3" = "ID_T_3",
         "ID_Sitze_T_4" = "ID_T_4", "ID_Sitze_T_5" = "ID_T_5") %>% 
  select(-c("ID_Sitze_T_4", "ID_Sitze_T_5")) %>% 
  left_join(bestandteile_komponente_all, by = c("ID_Motor" = "ID_K")) %>% 
  rename("ID_Motor_T_1" = "ID_T_1", "ID_Motor_T_2" = "ID_T_2", "ID_Motor_T_3" = "ID_T_3",
         "ID_Motor_T_4" = "ID_T_4", "ID_Motor_T_5" = "ID_T_5") %>% 
  select(-"ID_Motor_T_5")

rm(zulassungen_componentList, bestandteile_komponente_all)
```

### Finding relevant single part dataset
The following code is used to find the relevant single part for this study case.
```{r}
c(unique(substr(zulassungen_partList$ID_Karosserie_T_1, 1,2)), unique(substr(zulassungen_partList$ID_Karosserie_T_2, 1,2)),
  unique(substr(zulassungen_partList$ID_Karosserie_T_3, 1,2)), unique(substr(zulassungen_partList$ID_Karosserie_T_4, 1,2)),
  unique(substr(zulassungen_partList$ID_Karosserie_T_5, 1,2)),  unique(substr(zulassungen_partList$ID_Schaltung_T_1, 1,2)),
  unique(substr(zulassungen_partList$ID_Schaltung_T_2, 1,2)),  unique(substr(zulassungen_partList$ID_Schaltung_T_3, 1,2)),
  unique(substr(zulassungen_partList$ID_Sitze_T_1, 1,2)),  unique(substr(zulassungen_partList$ID_Sitze_T_2, 1,2)),
  unique(substr(zulassungen_partList$ID_Sitze_T_3, 1,2)),  unique(substr(zulassungen_partList$ID_Motor_T_1, 1,2)),
  unique(substr(zulassungen_partList$ID_Motor_T_2, 1,2)),  unique(substr(zulassungen_partList$ID_Motor_T_3, 1,2)),
  unique(substr(zulassungen_partList$ID_Motor_T_4, 1,2))) %>% 
  str_replace_all("-", "") %>% 
  as.numeric() %>% 
  na.omit() %>% 
  sort()
```
Based on the result above, all single part datasets are required for this study case.


### Creating a list of all relevant parts
```{r message = FALSE, warning = FALSE}
t01 <- select(zulassungen_partList, 10)
t02 <- select(zulassungen_partList, 11)
t03 <- select(zulassungen_partList, 12)
t04 <- select(zulassungen_partList, 13)
t05 <- select(zulassungen_partList, 14)
t06 <- select(zulassungen_partList, 15)
t07 <- select(zulassungen_partList, 16)
t08 <- select(zulassungen_partList, 17)
t09 <- select(zulassungen_partList, 18)
t10 <- select(zulassungen_partList, 19)
t11 <- select(zulassungen_partList, 20)
t12 <- select(zulassungen_partList, 21)
t13 <- select(zulassungen_partList, 22)
t14 <- select(zulassungen_partList, 23)
t15 <- select(zulassungen_partList, 24)

partList <- rbind(t01, t02, t03, t04, t05, 
                  t06, t07, t08, t09, t10, 
                  t11, t12, t13, t14, t15, 
                  use.names = FALSE) %>% rename("ID_T" = 1) %>% filter(!is.na(ID_T))

rm(t01, t02, t03, t04, t05, 
   t06, t07, t08, t09, t10,
   t11, t12, t13, t14, t15)
```


### Importing all component
During the importing of all component datasets, only the `ID` and `Fehlerhaft` column are relevant. The datasets are imported as follow.

#### Importing component K1xx (Motor)
Components are imported by using `fread` function of `data.table` package. For component K1BE1 and K1BE2, column 3 and 6 are selected. Since the dataset of component K1DI1 is structured with columns, that are repeated three times, column 3, 7, 10, 14, 17, and 21 are selected. By applying the function `merge_xyz()`, these columns could be merged into two relevant columns. To import component K1DI2, the original data needs to be read and some strings must be modified, so that the data could be imported as columns.
```{r message = FALSE, warning = FALSE}
komponente_k1be1 <- fread("Data/Komponente/Komponente_K1BE1.csv") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Motor" = "ID_K"))

komponente_k1be2 <- fread("Data/Komponente/Komponente_K1BE2.csv") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Motor" = "ID_K"))

komponente_k1di1 <- fread("Data/Komponente/Komponente_K1DI1.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_Motor = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Motor" = "ID_K"))

komponente_k1di2 <- read_file("Data/Komponente/Komponente_K1DI2.txt") %>% 
  str_replace_all("\t", "\n") %>% 
  fread(sep = "\\") %>% 
  select(3,6) %>% 
  semi_join(componentList, by = c("ID_Motor" = "ID_K"))
```

#### Importing component K2xx (Sitze/Seat)
The workflow of importing component K2xx is similar to component K1xx.
```{r message = FALSE, warning = FALSE}
komponente_k2le1 <- read_file("Data/Komponente/Komponente_K2LE1.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>% 
  str_replace_all("II", ";") %>% 
  fread() %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Sitze = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Sitze" = "ID_K"))

komponente_k2le2 <- fread("Data/Komponente/Komponente_K2LE2.txt", sep = "\\") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Sitze" = "ID_K"))

komponente_k2st1 <- fread("Data/Komponente/Komponente_K2ST1.txt") %>% select(3,7) %>% 
  semi_join(componentList, by = c("ID_Sitze" = "ID_K"))

komponente_k2st2 <- fread("Data/Komponente/Komponente_K2ST2.csv") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Sitze" = "ID_K"))
```

#### Importing component K3xx (Schaltung/Transmission)
```{r message = FALSE, warning = FALSE}
komponente_k3ag1 <- fread("Data/Komponente/Komponente_K3AG1.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_Schaltung = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Schaltung" = "ID_K"))

komponente_k3ag2 <- fread("Data/Komponente/Komponente_K3AG2.txt", sep = "\\") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Schaltung" = "ID_K"))

komponente_k3sg1 <- fread("Data/Komponente/Komponente_K3SG1.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Schaltung = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Schaltung" = "ID_K"))

komponente_k3sg2 <- fread("Data/Komponente/Komponente_K3SG2.csv") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Schaltung" = "ID_K"))
```

#### Importing component K4 - K7 (Karosserie)
```{r message = FALSE, warning = FALSE}
# Karosserie Dataset
komponente_k4 <- fread("Data/Komponente/Komponente_K4.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Karosserie = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Karosserie" = "ID_K"))

komponente_k5 <- fread("Data/Komponente/Komponente_K5.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_Karosserie = V1, Fehlerhaft = V2) %>% 
  semi_join(componentList, by = c("ID_Karosserie" = "ID_K"))

komponente_k6 <- fread("Data/Komponente/Komponente_K6.csv") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Karosserie" = "ID_K"))

komponente_k7 <- fread("Data/Komponente/Komponente_K7.txt") %>% select(3,6) %>% 
  semi_join(componentList, by = c("ID_Karosserie" = "ID_K"))
```

### Importing all single components

```{r message = FALSE, warning = FALSE}
# Single component dataset
einzelteil_t01 <- read_file("Data/Einzelteil/Einzelteil_T01.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>%
  str_replace_all(" ", "\n") %>% 
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T01 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T01" = "ID_T"))

einzelteil_t02 <- read_file("Data/Einzelteil/Einzelteil_T02.txt") %>% 
  str_replace_all("\t", "\n") %>%
  str_replace_all("  ", ";") %>% 
  fread() %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T02 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T02" = "ID_T"))

einzelteil_t03 <- read_file("Data/Einzelteil/Einzelteil_T03.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  str_replace_all("\\|", ";") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T03" = "ID_T"))

einzelteil_t04 <- fread("Data/Einzelteil/Einzelteil_T04.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T04" = "ID_T"))

einzelteil_t05 <- fread("Data/Einzelteil/Einzelteil_T05.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T05 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T05" = "ID_T"))

einzelteil_t06 <- fread("Data/Einzelteil/Einzelteil_T06.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T06" = "ID_T"))

einzelteil_t07 <- read_file("Data/Einzelteil/Einzelteil_T07.txt") %>% 
  str_replace_all("\"\"", "\"\n\"") %>% 
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T07" = "ID_T"))

einzelteil_t08 <- fread("Data/Einzelteil/Einzelteil_T08.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T08" = "ID_T"))

einzelteil_t09 <- read_file("Data/Einzelteil/Einzelteil_T09.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>% 
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T09 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T09" = "ID_T"))

einzelteil_t10 <- fread("Data/Einzelteil/Einzelteil_T10.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T10" = "ID_T"))

einzelteil_t11 <- read_file("Data/Einzelteil/Einzelteil_T11.txt") %>% 
  str_replace_all("\t", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T11" = "ID_T"))

einzelteil_t12 <- fread("Data/Einzelteil/Einzelteil_T12.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T12 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T12" = "ID_T"))

einzelteil_t13 <- fread("Data/Einzelteil/Einzelteil_T13.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T13" = "ID_T"))

einzelteil_t14 <- fread("Data/Einzelteil/Einzelteil_T14.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T14" = "ID_T"))

einzelteil_t15 <- fread("Data/Einzelteil/Einzelteil_T15.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T15 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T15" = "ID_T"))

einzelteil_t16 <- read_file("Data/Einzelteil/Einzelteil_T16.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("\t", "\n") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T16 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T16" = "ID_T"))

einzelteil_t17 <- fread("Data/Einzelteil/Einzelteil_T17.csv", dec = ",") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T17 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T17" = "ID_T"))

einzelteil_t18 <- fread("Data/Einzelteil/Einzelteil_T18.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T18" = "ID_T"))

einzelteil_t19 <- fread("Data/Einzelteil/Einzelteil_T19.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T19" = "ID_T"))

einzelteil_t20 <- read_file("Data/Einzelteil/Einzelteil_T20.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all(" ", "\n") %>% 
  fread() %>% 
  select(3, 6) %>% 
  semi_join(partList, by = c("ID_T20" = "ID_T"))

einzelteil_t21 <- fread("Data/Einzelteil/Einzelteil_T21.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T21" = "ID_T"))

einzelteil_t22 <- read_file("Data/Einzelteil/Einzelteil_T22.txt") %>% 
  str_replace_all("NA\"", "\n\"") %>%
  str_replace_all("\"\"", "\"\n\"") %>%
  str_replace_all("NA\t0\"", "NA\t0\n\"") %>%
  str_replace_all("(?<=\\d)\"(?=\\d)", "\n\"") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T22 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T22" = "ID_T"))

einzelteil_t23 <- fread("Data/Einzelteil/Einzelteil_T23.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T23 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T23" = "ID_T"))

einzelteil_t24 <- read_file("Data/Einzelteil/Einzelteil_T24.txt") %>% 
  str_replace_all("   ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T24 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T24" = "ID_T"))

einzelteil_t25 <- fread("Data/Einzelteil/Einzelteil_T25.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T25" = "ID_T"))

einzelteil_t26 <- fread("Data/Einzelteil/Einzelteil_T26.csv", dec = ",") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T26" = "ID_T"))

einzelteil_t27 <- read_file("Data/Einzelteil/Einzelteil_T27.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T27" = "ID_T"))

einzelteil_t30 <- fread("Data/Einzelteil/Einzelteil_T30.csv") %>% 
  select(3, 7, 10, 14, 17, 21) %>% 
  merge_xyz() %>% 
  rename(ID_T30 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T30" = "ID_T"))

einzelteil_t31 <- read_file("Data/Einzelteil/Einzelteil_T31.txt") %>% 
  str_replace_all("  ", ";") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T31" = "ID_T"))

einzelteil_t32 <- fread("Data/Einzelteil/Einzelteil_T32.csv", dec = ",") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T32 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T32" = "ID_T"))

einzelteil_t33 <- fread("Data/Einzelteil/Einzelteil_T33.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T33" = "ID_T"))

einzelteil_t34 <- read_file("Data/Einzelteil/Einzelteil_T34.txt") %>% 
  str_replace_all(" \\| \\| ", ";") %>% 
  str_replace_all("\"\"", "\"\n\"") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T34" = "ID_T"))

einzelteil_t35 <- read_file("Data/Einzelteil/Einzelteil_T35.txt") %>% 
  str_replace_all("\"\"", "\"\n\"") %>%
  str_replace_all("NA\"", "\n\"") %>%
  str_replace_all("(?<=\\d)\"(?=\\d)", "\n\"") %>%
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T35 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T35" = "ID_T"))

einzelteil_t36 <- read_file("Data/Einzelteil/Einzelteil_T36.txt") %>% 
  str_replace_all("  ", ";") %>% 
  str_replace_all(" ", "\n") %>%
  fread() %>% 
  select(3,6) %>% 
  semi_join(partList, by = c("ID_T36" = "ID_T"))

einzelteil_t37 <- fread("Data/Einzelteil/Einzelteil_T37.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T37" = "ID_T"))

einzelteil_t38 <- fread("Data/Einzelteil/Einzelteil_T38.csv") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T38 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T38" = "ID_T"))

einzelteil_t39 <- read_file("Data/Einzelteil/Einzelteil_T39.txt") %>% 
  str_replace_all("[:cntrl:]", "\n") %>%
  fread(sep = "\\") %>% 
  select(3, 7, 10, 14) %>% 
  merge_xy() %>% 
  rename(ID_T39 = V1, Fehlerhaft = V2) %>% 
  semi_join(partList, by = c("ID_T39" = "ID_T"))

einzelteil_t40 <- fread("Data/Einzelteil/Einzelteil_T40.csv") %>% select(3,6) %>% 
  semi_join(partList, by = c("ID_T40" = "ID_T"))


```

## 2. Data preparation

### Joining all components into a single dataset
```{r message = FALSE, warning = FALSE}
komponente_all <- rbind(komponente_k1be1, komponente_k1be2, komponente_k1di1, komponente_k1di2,
                        komponente_k2le1, komponente_k2le2, komponente_k2st1, komponente_k2st2,
                        komponente_k3ag1, komponente_k3ag2, komponente_k3sg1, komponente_k3sg2,
                        komponente_k4, komponente_k5, komponente_k6, komponente_k7,
                        use.names = FALSE) %>% rename(ID_K = 1)

rm(komponente_k1be1, komponente_k1be2, komponente_k1di1, komponente_k1di2,
   komponente_k2le1, komponente_k2le2, komponente_k2st1, komponente_k2st2,
   komponente_k3ag1, komponente_k3ag2, komponente_k3sg1, komponente_k3sg2,
   komponente_k4, komponente_k5, komponente_k6, komponente_k7,
   componentList)

```


### Joining all single parts into one single data:
```{r message = FALSE, warning = FALSE}
einzelteile_all <- rbind(einzelteil_t01,einzelteil_t02,einzelteil_t03,einzelteil_t04,einzelteil_t05,
                        einzelteil_t06,einzelteil_t07,einzelteil_t08,einzelteil_t09,einzelteil_t10,
                        einzelteil_t11,einzelteil_t12,einzelteil_t13,einzelteil_t14,einzelteil_t15,
                        einzelteil_t16,einzelteil_t17,einzelteil_t18,einzelteil_t19,einzelteil_t20,
                        einzelteil_t21,einzelteil_t22,einzelteil_t23,einzelteil_t24,einzelteil_t25,
                        einzelteil_t26,einzelteil_t27, einzelteil_t30,
                        einzelteil_t31,einzelteil_t32,einzelteil_t33,einzelteil_t34,einzelteil_t35,
                        einzelteil_t36,einzelteil_t37,einzelteil_t38,einzelteil_t39,einzelteil_t40, 
                        use.names = FALSE) %>% rename(ID_T = 1)

rm(einzelteil_t01,einzelteil_t02,einzelteil_t03,einzelteil_t04,einzelteil_t05,
   einzelteil_t06,einzelteil_t07,einzelteil_t08,einzelteil_t09,einzelteil_t10,
   einzelteil_t11,einzelteil_t12,einzelteil_t13,einzelteil_t14,einzelteil_t15,
   einzelteil_t16,einzelteil_t17,einzelteil_t18,einzelteil_t19,einzelteil_t20,
   einzelteil_t21,einzelteil_t22,einzelteil_t23,einzelteil_t24,einzelteil_t25,
   einzelteil_t26,einzelteil_t27, einzelteil_t30,
   einzelteil_t31,einzelteil_t32,einzelteil_t33,einzelteil_t34,einzelteil_t35,
   einzelteil_t36,einzelteil_t37,einzelteil_t38,einzelteil_t39,einzelteil_t40,
   partList)

```

## 3. Creation of final data set

### Joining combined vehicle registeration with whole component and single part dataset

```{r message = FALSE, warning = FALSE}
zulassungen_part <- zulassungen_partList %>% 
  left_join(komponente_all, by = c("ID_Karosserie" = "ID_K")) %>% 
  rename("Defective Karosserie" = Fehlerhaft) %>% 
  left_join(komponente_all, by = c("ID_Schaltung" = "ID_K")) %>% 
  rename("Defective Transmission" = Fehlerhaft) %>% 
  left_join(komponente_all, by = c("ID_Sitze" = "ID_K")) %>% 
  rename("Defective Seat" = Fehlerhaft) %>% 
  left_join(komponente_all, by = c("ID_Motor" = "ID_K")) %>% 
  rename("Defective Motor" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Karosserie_T_1" = "ID_T")) %>% 
  rename("Defective Part 1" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Karosserie_T_2" = "ID_T")) %>% 
  rename("Defective Part 2" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Karosserie_T_3" = "ID_T")) %>% 
  rename("Defective Part 3" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Karosserie_T_4" = "ID_T")) %>% 
  rename("Defective Part 4" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Karosserie_T_5" = "ID_T")) %>% 
  rename("Defective Part 5" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Schaltung_T_1" = "ID_T")) %>% 
  rename("Defective Part 6" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Schaltung_T_2" = "ID_T")) %>% 
  rename("Defective Part 7" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Schaltung_T_3" = "ID_T")) %>% 
  rename("Defective Part 8" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Sitze_T_1" = "ID_T")) %>% 
  rename("Defective Part 9" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Sitze_T_2" = "ID_T")) %>% 
  rename("Defective Part 10" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Sitze_T_3" = "ID_T")) %>% 
  rename("Defective Part 11" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Motor_T_1" = "ID_T")) %>% 
  rename("Defective Part 12" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Motor_T_2" = "ID_T")) %>% 
  rename("Defective Part 13" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Motor_T_3" = "ID_T")) %>% 
  rename("Defective Part 14" = Fehlerhaft) %>% 
  left_join(einzelteile_all, by = c("ID_Motor_T_4" = "ID_T")) %>% 
  rename("Defective Part 15" = Fehlerhaft) %>% 
  select(1:5, 25:43)

rm(einzelteile_all, komponente_all, zulassungen_partList)
```

### Counting number of defective components and single parts
```{r message = FALSE, warning = FALSE}
zulassungen_final <- zulassungen_part %>% 
  rowwise() %>% 
  mutate("Defective Components" = `Defective Karosserie` + `Defective Transmission` + `Defective Seat` + `Defective Motor`) %>% 
  mutate("Defective Parts" = sum(`Defective Part 1`, `Defective Part 2`, `Defective Part 3`, `Defective Part 4`, 
           `Defective Part 5`, `Defective Part 6`, `Defective Part 7`, `Defective Part 8`, `Defective Part 9`, 
           `Defective Part 10`, `Defective Part 11`, `Defective Part 12`, `Defective Part 13`, `Defective Part 14`,
           `Defective Part 15`, na.rm = TRUE))
```

### Updating the defective data of vehicle and components
If any component inside the vehicle is defect, then the vehicle should be marked as defective respectively, even though the data from the OEM indicates otherwise. Similar logic applies to the part level. For example, if any of part 1, 2, 3, 4, or 5 (which are all parts of karosserie) is defect, then karosserie must be marked as defect.
```{r message = FALSE, warning = FALSE}
zulassungen_final$`Defective Karosserie` <- replace(zulassungen_final$`Defective Karosserie`,
                                                      zulassungen_final$`Defective Part 1` > 0 | 
                                                        zulassungen_final$`Defective Part 2` > 0| 
                                                        zulassungen_final$`Defective Part 3` > 0| 
                                                        zulassungen_final$`Defective Part 4` > 0| 
                                                        zulassungen_final$`Defective Part 5` > 0,
                                                      1)

zulassungen_final$`Defective Transmission` <- replace(zulassungen_final$`Defective Transmission`,
                                                      zulassungen_final$`Defective Part 6` > 0 | 
                                                        zulassungen_final$`Defective Part 7` > 0| 
                                                        zulassungen_final$`Defective Part 8` > 0,
                                                      1)

zulassungen_final$`Defective Seat` <- replace(zulassungen_final$`Defective Seat`,
                                                      zulassungen_final$`Defective Part 9` > 0 | 
                                                        zulassungen_final$`Defective Part 10` > 0| 
                                                        zulassungen_final$`Defective Part 11` > 0,
                                                      1)

zulassungen_final$`Defective Motor` <- replace(zulassungen_final$`Defective Motor`,
                                                      zulassungen_final$`Defective Part 12` > 0 | 
                                                        zulassungen_final$`Defective Part 13` > 0| 
                                                        zulassungen_final$`Defective Part 14` > 0| 
                                                        zulassungen_final$`Defective Part 15` > 0,
                                                      1)

zulassungen_final$`Defective Vehicle` <- replace(zulassungen_final$`Defective Vehicle`,
                                                      zulassungen_final$`Defective Karosserie` > 0 | 
                                                        zulassungen_final$`Defective Transmission` > 0| 
                                                        zulassungen_final$`Defective Seat` > 0| 
                                                        zulassungen_final$`Defective Motor` > 0,
                                                      1)

```



### Counting number of components and single parts in each vehicle
```{r message = FALSE, warning = FALSE}
zulassungen_final$`Number of Components` <- rowSums(!is.na(zulassungen_part[,6:9]))
zulassungen_final$`Number of Parts` <- rowSums(!is.na(zulassungen_part[,10:24]))
```

### Selecting relevant columns and summarize based on OEM Number, Registeration Date and Location
```{r message = FALSE, warning = FALSE}
final_data <- zulassungen_final %>% 
  select(1:5, 27, 25, 28, 26)

final_data <- final_data %>% 
  group_by(Herstellernummer, Zulassung, Gemeinden) %>% 
  summarize("Number of Vehicle" = n(),
            "Defective Vehicle" = sum(`Defective Vehicle`),
            "Number of Components" = sum(`Number of Components`),
            "Defective Components" = sum(`Defective Components`),
            "Number of Parts" = sum(`Number of Parts`),
            "Defective Parts" = sum(`Defective Parts`))


rm(zulassungen_part, zulassungen_final)
```

### Export dataset to folder
```{r message = FALSE, warning = FALSE}
write_csv(final_data, "Final_dataset_group_07.csv")
```

